\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{paracol}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Tighter margins for a dense two-column layout
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Subtle palette
\definecolor{boxbg}{HTML}{F2F3F5}   % very light cool-gray panel
\definecolor{accent}{HTML}{2B3A55}  % restrained dark slate

% Two-column geometry: left sidebar = 1/3, main = 2/3
\setlength{\columnsep}{0.05\textwidth}
\columnratio{0.31}

% Soft shaded panel behind the left sidebar
\backgroundcolor{c[0](-12pt,-14pt)(12pt,14pt)}{boxbg}

% Section formatting (subtle slate rule)
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{accent}\titlerule \vspace{-6pt}]

\pdfgentounicode=1

%-------------------------
\newcommand{\spacing}{-0.44cm}

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-2pt}}}
}

% Experience / research subheading sized to the current column width
\newcommand{\resumeSubheading}[4]{
  \vspace{0pt}\item
    \begin{tabular*}{1.0\linewidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\small #2} \\
    \end{tabular*}
    \vspace{1pt}
    {\small\textit{#3 ~$\vert$~ #4}}
    \vspace{-4pt}
}

% Education entry for the sidebar (stacked, no right column)
\newcommand{\eduItem}[4]{
  \vspace{1pt}
  {\textbf{#1}}\\
  {\small #2}\\
  {\footnotesize\textit{#3}}\\
  {\footnotesize #4}
  \vspace{4pt}
}

% Sidebar skill block: bold category, then comma list beneath
\newcommand{\skillBlock}[2]{
  \vspace{2pt}
  {\small\textbf{#1}}\\
  {\small #2}
  \vspace{3pt}
}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{\spacing}}
\newcommand{\resumeItemListStart}{\begin{itemize}[itemsep=0pt, parsep=0pt, topsep=1pt, leftmargin=0.13in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%%%%%%  RESUME STARTS HERE  %%%%%%

\begin{document}

\newcommand{\name}{Nathan Ludlow}
\newcommand{\role}{Robotics Software Engineer}
\newcommand{\workemail}{nateludlow@gmail.com}
\newcommand{\linkedin}{linkedin.com/in/nathan-ludlow}
\newcommand{\website}{natelud.github.io}

%----------HEADING (full width)----------
\begin{center}
    {\Huge \scshape \name} \\ \vspace{3pt}
    {\large \scshape \role} \\ \vspace{3pt}
    \small
    \href{mailto:\workemail}{\underline{\workemail}} ~$\vert$~
    \href{https://\linkedin}{\underline{\linkedin}} ~$\vert$~
    \href{https://\website}{\underline{\website}}
\end{center}
\vspace{2pt}

%----------SUMMARY / STORY (full width panel)----------
{\setlength{\fboxsep}{6pt}%
\noindent\colorbox{boxbg}{%
\begin{minipage}{\dimexpr\textwidth-2\fboxsep\relax}
\small
I am a robotics software engineer who started in mechanical design and grew into full-stack autonomy. Over two years in industry I built perception, planning, and control software for industrial robot arms, including a domain-specific language that let LLMs program manipulators from natural language. Across four years of research I have published in reinforcement learning, autonomous driving, and physical human-robot collaboration, and I now want to bring that range to a team shipping real-world robotics.
\end{minipage}}}
\vspace{-12pt}

%====================================================================
\begin{paracol}{2}

%%%%%%%%%%%%%%%%%%%%%% LEFT SIDEBAR (1/3) %%%%%%%%%%%%%%%%%%%%%%

\section{Technical Skills}
\vspace{2pt}

\skillBlock{Programming}{Python, C++, C, Rust, Julia, MATLAB, Java}

\skillBlock{ML / RL}{PyTorch, JAX / JaxMARL, TensorFlow, RLlib, Gymnasium, Weights \& Biases; multi-agent \& cooperative RL}

\skillBlock{Robotics}{ROS / ROS2, Gazebo, MuJoCo, PyBullet, OpenCV, RealSense SDK}

\skillBlock{Methods}{Perception (Kalman/EKF, point-cloud processing, pose estimation); planning (RRT, A*, MPPI, trajectory optimization); control (MPC, control barrier functions, LQR, impedance control); knowledge-graph reasoning, LLM integration}

\skillBlock{Robot Platforms}{Yaskawa, xArm, Universal Robots, Franka Panda, KUKA, Farm-ng}

\skillBlock{Hardware / CAD}{SolidWorks (Certified), Onshape, Inventor, strain-gauge sensing, embedded control}

\skillBlock{Tools}{Linux, Git, Docker, CUDA, \LaTeX}

\skillBlock{Languages}{English (Native), Spanish (Fluent)}

\vspace{8pt}

\section{Education}
\vspace{4pt}

\eduItem{Carnegie Mellon University}
        {M.S.\ in Robotics}
        {Advised by Dr.\ Katia Sycara \textbf{|} GPA 4.00/4.00}
        {Expected Jul.\ 2026 \textbf{·} Pittsburgh, PA}

\eduItem{Brigham Young University}
        {B.S.\ in Mechanical Engineering}
        {Emphasis: Dynamics, Controls, Robotics}
        {Minors: CS, Math \textbf{|} GPA 3.79/4.00}

\vspace{1pt}
{\footnotesize Apr.\ 2024 \textbf{·} Provo, UT}

%%%%%%%%%%%%%%%%%%%%%% RIGHT MAIN COLUMN (2/3) %%%%%%%%%%%%%%%%%%%%%%
\switchcolumn

\section{Industry Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Altitude AI}{May 2022 -- Sep.\ 2023}
      {Robotics Software Engineer}{Salt Lake City, UT}
      \resumeItemListStart
        \resumeItem{\textbf{Automated meat processing:} Built the perception, path-planning, and control pipeline for robotic pork-belly skin removal, coordinating industrial arms with electric cutting tools on variable, deformable workpieces in production.}
        \resumeItem{\textbf{Natural-language robot programming:} Designed a domain-specific language that let LLMs generate executable code for industrial arms from natural-language instructions, enabling customers to rapidly create and modify custom tasks on our hardware platforms and accelerating manipulation-task prototyping.}
        \resumeItem{Deployed a pick-and-place robotic system at a customer facility, and ran on-site deployment tests of the pork-skinning system to validate performance under real production conditions.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

\section{Research Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {CMU Advanced Agent Robotics (AART) Lab}{Sep.\ 2024 -- Present}
      {Graduate Research Assistant --- Dr.\ Katia Sycara}{Pittsburgh, PA}
      \resumeItemListStart
        \resumeItem{Developed Knowledge Graph-Augmented Reinforcement Learning (KG-RL), leveraging semantic relationships for cooperative multi-agent tasks; demonstrated up to \textbf{3$\times$ faster convergence} and improved final performance across Overcooked-AI, MiniGrid, Craftax, and AI-Habitat. \textit{First-author submission under review.}}
        \resumeItem{Extending KG-RL to temporal knowledge graphs with attention-based and recurrent encoders (Time2Vec, Time-LSTM) to reason over dynamic state evolution and temporal dependencies.}
        \resumeItem{Engineered a vectorized JAX / JaxMARL training stack on lab GPU servers, building reproducible PPO training and evaluation pipelines for multi-agent benchmarks.}
      \resumeItemListEnd


    \resumeSubheading
      {CMU Driverless Intelligent Vehicles (DRIVE) Lab}{Jun.\ 2023 -- Aug.\ 2024}
      {RISS Research Fellow \& Research Assistant --- Dr.\ John M.\ Dolan}{Pittsburgh, PA}
      \resumeItemListStart
        \resumeItem{Designed a hierarchical risk-aware behavioral model for simulating human drivers in AV testing, introducing a forward-looking Gaussian risk metric with social-pooling trajectory prediction. \textit{First-author publication at ICRA 2024.}}
        \resumeItem{Developed a risk-aware Voronoi-cell approach inspired by control barrier functions for safe multi-agent navigation around dynamic obstacles under motion uncertainty.}
      \resumeItemListEnd


    \resumeSubheading
      {BYU Robotics And Dynamics (RAD) Laboratory}{Feb.\ 2022 -- Jun.\ 2024}
      {Research Assistant --- Dr.\ Marc Killpack \& Dr.\ John Salmon}{Provo, UT}
      \resumeItemListStart
        \resumeItem{Developed dynamic control methods for physical human-robot co-manipulation of large objects (cooperative swinging, throwing, tossing) and built the full hardware/software architecture for an omnidirectional mobile base. \textit{UCUR 2023.}}
        \resumeItem{Built a VR platform with force sensing to analyze human-human interaction dynamics during cooperative manipulation.}
      \resumeItemListEnd


    \resumeSubheading
      {BYU Crop Biomechanics Laboratory}{Sep.\ 2023 -- Apr.\ 2024}
      {Capstone Team Lead --- Dr.\ Douglas Cook}{Provo, UT}
      \resumeItemListStart
        \resumeItem{Led a team building an autonomous robotic system to measure maize-stalk stiffness in the field, designing a novel strain-gauge sensor package, processing algorithms, and navigation control. \textit{Publication in MDPI Sensors 2025.}}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

\section{Publications}
      \resumeItemListStart
        \resumeItem{\textbf{N.\ Ludlow}, V.\ Tadiparthi, H.\ N.\ Mahjoub, Y.\ Xie, W.\ Kim, K.\ Sycara, S.\ Stepputtis. ``Knowledge Graph-Augmented Reinforcement Learning.'' \textit{TMLR}, 2026. \textit{Under review.}}
        \resumeItem{\textbf{N.\ Ludlow}, A.\ Krieger, M.\ Menon, J.\ Chandrachud. ``Strategy Search for Human-Robot Teaming.'' \textit{CHAI Workshop}, UC Berkeley, 2026. \textit{To appear.}}
        \resumeItem{C.\ Noh, K.\ Smith, \ldots, \textbf{N.\ Ludlow}, \ldots, D.\ Cook. \href{https://doi.org/10.3390/s25216561}{``Measurement of Force and Position Using a Cantilever Beam and Multiple Strain Gauges.''} \textit{MDPI Sensors}, 2025.}
        \resumeItem{\textbf{N.\ Ludlow}, Y.\ Lyu, J.\ M.\ Dolan. \href{https://ieeexplore.ieee.org/document/10610354}{``Hierarchical Learned Risk-Aware Planning Framework for Human Driving Modeling.''} \textit{ICRA}, 2024.}
        \resumeItem{\textbf{N.\ Ludlow}, M.\ D.\ Killpack, J.\ L.\ Salmon. \href{https://our.utah.edu/ucur/mobile-base-for-physical-human-robot-interaction-and-co-manipulation/}{``Mobile Base for Physical Human-Robot Interaction and Co-manipulation.''} \textit{UCUR}, 2023.}
      \resumeItemListEnd

\end{paracol}

\end{document}
